---
title: "Minutes Analysis"
author: "Connor Krenzer"
date: "1/4/2021"
output: html_document
---
## Introduction
Provide some background, explain what the Fed Minutes are, etc... then describe the data you will be analyzing

The data included in this analysis includes all FOMC Minutes between January 28th, 2009 to November 5th, 2020 (inclusive).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      results = "hide",
                      error = F,
                      warning = F,
                      message = F)
```

## Packages

Note that I am using the pacman package here, because it incorporates the installing and loading of packages quite nicely.
```{r, echo = TRUE}
if(!require(pacman)) install.packages("pacman")
pacman::p_load(tidytext, dplyr, readtext)

```

## Data Import
Describe how you will import your data and how you will organize it--import the obama-era data, add an identifier, such as "Obama" column, a date column, then do the same for the trump era.